### 2022-07-31 message-from-committee.tex
Updated name and email use in front matter, paper, and reference to prior work.

\begin{tabular}{r r p{0.5\linewidth}}
	Asher Trockman (general chair) &
Jenny Lin (easy chair)\\
	Siva Somayyajula (senior hard-ass chair) &
Sol Boucher (acting emeritus proceedings chair)\\
	Brandon Bohrer (beanbag chair) &
Ryan Kavanagh (rockin' chair)\\
	Stefan Muller (ergonomic office chair) &
Chris Yu (art chair)\\
	Hana Frluckaj (moderation chair) &
Daniel Smullen (moderation chair)\\
	Xindi Wu (conference chair) &
Sydney Gibson (tweet chair)\\
	John Grosen (archaeology chair) &
	Vivian Shen (honorary awards chair)
\end{tabular}

@@

%\bibliographystyle{acm}
%\bibliography{msgrefs}
%\thispagestyle{empty}

>>>>

\begin{tabular}{r r p{0.5\linewidth}}
	Asher Trockman (general chair) &
Jenny Lin (easy chair)\\
	Siva Somayyajula (senior hard-ass chair) &
Sol Boucher (acting emeritus proceedings chair)\\
	Rose Bohrer (beanbag chair) &
Ryan Kavanagh (rockin' chair)\\
	Stefan Muller (ergonomic office chair) &
Chris Yu (art chair)\\
	Hana Frluckaj (moderation chair) &
Daniel Smullen (moderation chair)\\
	Xindi Wu (conference chair) &
Sydney Gibson (tweet chair)\\
	John Grosen (archaeology chair) &
	Vivian Shen (honorary awards chair)
\end{tabular}

@@

%\bibliographystyle{acm}
%\bibliography{msgrefs}
\thispagestyle{empty}
